My topic is on the study of formal languages and automata theory. This topic is an intersection of mathematics and theoretical computer science. It explores the relationship between
algebraic structures and computational models, providing a rigorous framework for understanding the capabilities and limitations of different types of automata and the languages they recognize.

A DFA, or Deterministic Finite Automata, is a theoretical model of computation that consists of a finite set of states, an input alphabet, a transition function, a start state, and a set of accept states. A DFA can also be viewed as a generator of algebraic information.
A regular language $L$ has associated with it a monoid $M(L)$ called the syntactic monoid of L.
Monoids help us determine the class of regular recognizable languages.

My first objective is to understand the algebraic structure of $M(L)$ and then use this to study varieties and pseudovarieties of monoids.
A variety of algebras is a class of algebras closed under the formation of homomorphic images, subalgebras, and arbitrary direct products. When restricted to finite algebras, these are called pseudovarieties.

The next objective is to explore Eilenberg's correspondence, which establishes a bijective relationship between varieties of regular languages and pseudovarieties of finite monoids.
This correspondence allows us to translate problems in language theory into problems in algebra and vice versa, providing powerful tools for analysis. Under this correspondence, a regula language $L$
belongs to a variety of languages $\mathcal{V}$ if and only if its syntactic monoid $M(L)$ belongs to the corresponding pseudovariety of monoids $\mathcal{W}$.

This connection is useful in classifying regular languages based on the algebraic properties of their syntactic monoids.

Finally I would like to look into the membership problem for pseudovarieties of finite monoids. Which is the problem of determining whether a given finite monoid belongs to a specified pseudovariety.
This problem has significant implications in automata theory and formal language theory. I would also like to look into algorithms used in the membership problem for certain pseudovarities.

\begin{framed}
    The aim of this project is to explore pseudovarieties of finite monoids and their applications in formal languages and automata theory.
\end{framed}
The classification of regular languages using algebraic structures is a fascinating area of study and has implications
in many areas of maths and computer science. Additionally, the membership problem for pseudovarieties of finite monoids is a challenging and interesting problem that has practical applications in automata theory and formal language theory.